Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-13 grove-paper.tex
add informal definition of simple cycles (Eric Griffis)

\subsubsection{Graph Actions}
\label{sub:Graph Actions}

@@

\subsection{Edit Actions}
\label{sub:Edit Actions}

@@

\[
\begin{array}{l}
  \textrm{Edit Actions}: \grave{e} \in Act ::= e \mid \#u \mid \conflict{\grave{e}}{\grave{e}} \\
  \s : \G \to Act \times \V^{*} \times \V^{*} \times \V^{*} \\
  \s(G) = (\grave{e}, \MP(G), \CC(G), \D(G)) \\
  \MP(G) = \left\{ v \in \vertexes(G) \mid \exists e_1,e_2 \in \liveEdges(G), e_1= \right. \\
      \qquad \left. (v,p_1,v_1), e_2=(v,p_2,v_2), e_1 \ne e_2 \right\} \\
  \CC(G) = \ldots \\
  \D(G) = \orphans(G) \setminus \left\{ v_0 \right\} \\
  \orphans(G) = \left\{ v \in \vertexes(G) \mid \forall e=(v^\prime,p,v^{\prime\prime}) \in \right. \\
      \qquad \left. \liveEdges(G), v^{\prime\prime} \ne v \right\} \\
  \vertexes(G) = \left\{ v \mid \exists e = (v^\prime, p, v^{\prime\prime}) \in \edges(G), v \in \left\{ v^\prime, v^{\prime\prime}\right\} \right\} \\
  \edges(G) = \left\{ e \mid G(e) \ne \bot \right\} \\
  \liveEdges(G) = \left\{ e \mid G(e) = + \right\} \\
\end{array}
\]

>>>>

\subsubsection{Graph Edits}
\label{sub:Graph Edits}

@@

\subsection{Graph Decomposition}
\label{sub:Graph Decomposition}

What does a graph decomposition produce? a 4-tuple (reachable, multiparented, deleted, simple cycles).

A simple cycle is a set of vertices connected by a closed path, consisting
   of:

   1) two or more vertices, all descendants of each other, and
   2) the vertices of any non-multiparent subtrees reachable from the core, and
      not reachable from the root vertex.

  To determine the simple cycles of a graph, we:

  1) check if any vertex in the graph is a descendant of itself or some other
     vertex that is (a descendant of itself),
  2) find the least vertex in the core of this new(ly discovered) cycle, and
  3) return a tree connecting every vertex reachable from the least (vertex).

  The least vertex of a cycle is the one that was created first. To ensure consistent behavior, the search for reachable vertices begins at the least vertex in a cycle.

<Mathematical definition of above.>

\subsection{User Actions}
\label{sub:User Actions}

@@

\[
\begin{array}{l}
  \textrm{User Actions}: \grave{e} \in Act ::= e \mid \#u \mid \conflict{\grave{e}}{\grave{e}} \\
  \s : \G \to Act \times \V^{*} \times \V^{*} \times \V^{*} \\
  \s(G) = (\grave{e}, \MP(G), \CC(G), \D(G)) \\
  \MP(G) = \left\{ v \in \vertexes(G) \mid \exists e_1,e_2 \in \liveEdges(G), e_1= \right. \\
      \qquad \left. (v,p_1,v_1), e_2=(v,p_2,v_2), e_1 \ne e_2 \right\} \\
  \CC(G) = \ldots \\
  \D(G) = \orphans(G) \setminus \left\{ v_0 \right\} \\
  \orphans(G) = \left\{ v \in \vertexes(G) \mid \forall e=(v^\prime,p,v^{\prime\prime}) \in \right. \\
      \qquad \left. \liveEdges(G), v^{\prime\prime} \ne v \right\} \\
  \vertexes(G) = \left\{ v \mid \exists e = (v^\prime, p, v^{\prime\prime}) \in \edges(G), v \in \left\{ v^\prime, v^{\prime\prime}\right\} \right\} \\
  \edges(G) = \left\{ e \mid G(e) \ne \bot \right\} \\
  \liveEdges(G) = \left\{ e \mid G(e) = + \right\} \\
\end{array}
\]
